Automatically Exploring Hypothesis Spaces

### 2018-04-29 test.tex
some more problem solutions

\emph{Catalan:}\\\begin{longtable}{ll|l}\toprule
$\varnothing$ $+$stem$+$ $\varnothing$ & $\varnothing$ $+$stem$+$ \textipa{@} & UR
\\ \midrule
\textipa{@kelj} & \textipa{@kelj@} & \textipa{@kelj}\\
\textipa{mal} & \textipa{mal@} & \textipa{mal}\\
\textipa{siBil} & \textipa{siBil@} & \textipa{siBil}\\
\textipa{@skerp} & \textipa{@skerp@} & \textipa{@skerp}\\
\textipa{Sop} & \textipa{Sop@} & \textipa{Sop}\\
\textipa{sEk} & \textipa{sEk@} & \textipa{sEk}\\
\textipa{@spEs} & \textipa{@spEs@} & \textipa{@spEs}\\
\textipa{gros} & \textipa{gros@} & \textipa{gros}\\
\textipa{baS} & \textipa{baS@} & \textipa{baS}\\
\textipa{koS} & \textipa{koS@} & \textipa{koS}\\
\textipa{tot} & \textipa{tot@} & \textipa{tot}\\
\textipa{brut} & \textipa{brut@} & \textipa{brut}\\
\textipa{pOk} & \textipa{pOk@} & \textipa{pOk}\\
\textipa{pr@sis} & \textipa{pr@siz@} & \textipa{pr@siz}\\
\textipa{fr@nses} & \textipa{fr@nsez@} & \textipa{fr@nsez}\\
\textipa{gris} & \textipa{griz@} & \textipa{griz}\\
\textipa{k@zat} & \textipa{k@zaD@} & \textipa{k@zad}\\
\textipa{bwit} & \textipa{bwiD@} & \textipa{bwid}\\
\textipa{rOt\super S} & \textipa{rOZ@} & \textipa{rOd\super Z}\\
\textipa{bot\super S} & \textipa{boZ@} & \textipa{bod\super Z}\\
\textipa{orp} & \textipa{orB@} & \textipa{orb}\\
\textipa{ljark} & \textipa{ljarG@} & \textipa{ljarg}\\
\textipa{sek} & \textipa{seG@} & \textipa{seg}\\
\textipa{f@Suk} & \textipa{f@SuG@} & \textipa{f@Sug}\\
\textipa{grok} & \textipa{groG@} & \textipa{grog}\\
\textipa{puruk} & \textipa{puruG@} & \textipa{purug}\\
\textipa{kandit} & \textipa{kandiD@} & \textipa{kandid}\\
\textipa{frEt} & \textipa{frED@} & \textipa{frEd}\\
\textipa{s@Gu} & \textipa{s@Gur@} & \textipa{s@Gur}\\
\textipa{du} & \textipa{dur@} & \textipa{dur}\\
\textipa{s@G@Do} & \textipa{s@G@Dor@} & \textipa{s@g@Dor}\\
\textipa{kla} & \textipa{klar@} & \textipa{klar}\\
\textipa{nu} & \textipa{nu@} & \textipa{nu}\\
\textipa{kru} & \textipa{kru@} & \textipa{kru}\\
\textipa{flO\~nd\super Zu} & \textipa{flO\~nd\super Z@} & \textipa{flO\~nd\super Zu}\\
\textipa{dropu} & \textipa{drop@} & \textipa{dropu}\\
\textipa{@gzakt@} & \textipa{@gzakt@} & \textipa{@gzakt@}\\
\textipa{@lBi} & \textipa{@lBin@} & \textipa{@lBin}\\
\textipa{sa} & \textipa{san@} & \textipa{san}\\
\textipa{pla} & \textipa{plan@} & \textipa{plan}\\
\textipa{bo} & \textipa{bon@} & \textipa{bon}\\
\textipa{s@rE} & \textipa{s@rEn@} & \textipa{s@rEn}\\
\textipa{suBlim} & \textipa{suBlim@} & \textipa{suBlim}\\
\textipa{al} & \textipa{alt@} & \textipa{alt}\\
\textipa{fOr} & \textipa{fOrt@} & \textipa{fOrt}\\
\textipa{kur} & \textipa{kurt@} & \textipa{kurt}\\
\textipa{sor} & \textipa{sorD@} & \textipa{sord}\\
\textipa{bEr} & \textipa{bErD@} & \textipa{bErd}\\
\textipa{san} & \textipa{sant@} & \textipa{sant}\\
\textipa{k@lEn} & \textipa{k@lEnt@} & \textipa{k@lEnt}\\
\textipa{prufun} & \textipa{prufund@} & \textipa{prufund}\\
\textipa{f@kun} & \textipa{f@kund@} & \textipa{f@kund}\\
\textipa{d@sen} & \textipa{d@sent@} & \textipa{d@sent}\\
\textipa{dulen} & \textipa{dulent@} & \textipa{dulent}\\
\textipa{@stuDian} & \textipa{@stuDiant@} & \textipa{@stuDEiant}\\
\textipa{blaN} & \textipa{blaNk@} & \textipa{blaN\~n}\\
\bottomrule\end{longtable}
\begin{tabular}{l}\emph{Rules: }\\
\verb|[-lateral +sonorant +coronal]| $\to$ $\varnothing$ /  \verb|_| \#\\\verb|[-sonorant]| $\to$ \verb|[-voice]| /  \verb|_| \#\\\verb|[-vowel]| $\to$ \textipa{k} / \textipa{N} \verb|_| \\\verb|[-nasal +voice]| $\to$ \verb|[+continuant]| / \verb|[-nasal]| \verb|_| \verb|[+vowel]|\\\verb|[+vowel]| $\to$ $\varnothing$ / \verb|[-sonorant]| \verb|_| \verb|[+vowel]|\\\textipa{t} $\to$ $\varnothing$ / \verb|[-vowel]| \verb|_| \#
\end{tabular}

>>>>

\emph{Catalan:}\\\begin{longtable}{ll|l}\toprule
$\varnothing$ $+$stem$+$ $\varnothing$ & $\varnothing$ $+$stem$+$ \textipa{@} & UR
\\ \midrule
\textipa{@kelj} & \textipa{@kelj@} & \textipa{@kelj}\\
\textipa{mal} & \textipa{mal@} & \textipa{mal}\\
\textipa{siBil} & \textipa{siBil@} & \textipa{siBil}\\
\textipa{@skerp} & \textipa{@skerp@} & \textipa{@skerp}\\
\textipa{Sop} & \textipa{Sop@} & \textipa{Sop}\\
\textipa{sEk} & \textipa{sEk@} & \textipa{sEk}\\
\textipa{@spEs} & \textipa{@spEs@} & \textipa{@spEs}\\
\textipa{gros} & \textipa{gros@} & \textipa{gros}\\
\textipa{baS} & \textipa{baS@} & \textipa{baS}\\
\textipa{koS} & \textipa{koS@} & \textipa{koS}\\
\textipa{tot} & \textipa{tot@} & \textipa{tot}\\
\textipa{brut} & \textipa{brut@} & \textipa{brut}\\
\textipa{pOk} & \textipa{pOk@} & \textipa{pOk}\\
\textipa{pr@sis} & \textipa{pr@siz@} & \textipa{pr@siz}\\
\textipa{fr@nses} & \textipa{fr@nsez@} & \textipa{fr@nsez}\\
\textipa{gris} & \textipa{griz@} & \textipa{griz}\\
\textipa{k@zat} & \textipa{k@zaD@} & \textipa{k@zad}\\
\textipa{bwit} & \textipa{bwiD@} & \textipa{bwid}\\
\textipa{rOt\super S} & \textipa{rOZ@} & \textipa{rOd\super Z}\\
\textipa{bot\super S} & \textipa{boZ@} & \textipa{bod\super Z}\\
\textipa{orp} & \textipa{orB@} & \textipa{orb}\\
\textipa{ljark} & \textipa{ljarG@} & \textipa{ljarg}\\
\textipa{sek} & \textipa{seG@} & \textipa{seg}\\
\textipa{f@Suk} & \textipa{f@SuG@} & \textipa{f@Sug}\\
\textipa{grok} & \textipa{groG@} & \textipa{grog}\\
\textipa{puruk} & \textipa{puruG@} & \textipa{purug}\\
\textipa{kandit} & \textipa{kandiD@} & \textipa{kandid}\\
\textipa{frEt} & \textipa{frED@} & \textipa{frEd}\\
\textipa{s@Gu} & \textipa{s@Gur@} & \textipa{s@Gur}\\
\textipa{du} & \textipa{dur@} & \textipa{dur}\\
\textipa{s@G@Do} & \textipa{s@G@Dor@} & \textipa{s@g@Dor}\\
\textipa{kla} & \textipa{klar@} & \textipa{klar}\\
\textipa{nu} & \textipa{nu@} & \textipa{nu}\\
\textipa{kru} & \textipa{kru@} & \textipa{kru}\\
\textipa{flO\~nd\super Zu} & \textipa{flO\~nd\super Z@} & \textipa{flO\~nd\super Zu}\\
\textipa{dropu} & \textipa{drop@} & \textipa{dropu}\\
\textipa{@gzakt@} & \textipa{@gzakt@} & \textipa{@gzakt@}\\
\textipa{@lBi} & \textipa{@lBin@} & \textipa{@lBin}\\
\textipa{sa} & \textipa{san@} & \textipa{san}\\
\textipa{pla} & \textipa{plan@} & \textipa{plan}\\
\textipa{bo} & \textipa{bon@} & \textipa{bon}\\
\textipa{s@rE} & \textipa{s@rEn@} & \textipa{s@rEn}\\
\textipa{suBlim} & \textipa{suBlim@} & \textipa{suBlim}\\
\textipa{al} & \textipa{alt@} & \textipa{alt}\\
\textipa{fOr} & \textipa{fOrt@} & \textipa{fOrt}\\
\textipa{kur} & \textipa{kurt@} & \textipa{kurt}\\
\textipa{sor} & \textipa{sorD@} & \textipa{sord}\\
\textipa{bEr} & \textipa{bErD@} & \textipa{bErd}\\
\textipa{san} & \textipa{sant@} & \textipa{sant}\\
\textipa{k@lEn} & \textipa{k@lEnt@} & \textipa{k@lEnt}\\
\textipa{prufun} & \textipa{prufund@} & \textipa{prufund}\\
\textipa{f@kun} & \textipa{f@kund@} & \textipa{f@kund}\\
\textipa{d@sen} & \textipa{d@sent@} & \textipa{d@sent}\\
\textipa{dulen} & \textipa{dulent@} & \textipa{dulent}\\
\textipa{@stuDian} & \textipa{@stuDiant@} & \textipa{@stuDEiant}\\
\textipa{blaN} & \textipa{blaNk@} & \textipa{blaN\~n}\\
\bottomrule\end{longtable}
\begin{tabular}{l}\emph{Rules: }\\
\verb|[-lateral +sonorant +coronal]| $\to$ $\varnothing$ /  \verb|_| \#\\\verb|[-sonorant]| $\to$ \verb|[-voice]| /  \verb|_| \#\\\verb|[-vowel]| $\to$ \textipa{k} / \textipa{N} \verb|_| \\\verb|[-nasal +voice]| $\to$ \verb|[+continuant]| / \verb|[-nasal]| \verb|_| \verb|[+vowel]|\\\verb|[+vowel]| $\to$ $\varnothing$ / \verb|[-sonorant]| \verb|_| \verb|[+vowel]|\\\textipa{t} $\to$ $\varnothing$ / \verb|[-vowel]| \verb|_| \#
\end{tabular}
\emph{Korean:}\\\begin{longtable}{lllllllllllll|l}\toprule
$\varnothing$ $+$stem$+$ \textipa{man} & $\varnothing$ $+$stem$+$ \textipa{maNk\super h1m} & $\varnothing$ $+$stem$+$ \textipa{nar1m} & $\varnothing$ $+$stem$+$ $\varnothing$ & $\varnothing$ $+$stem$+$ \textipa{tero} & $\varnothing$ $+$stem$+$ \textipa{kwa} & $\varnothing$ $+$stem$+$ \textipa{pota} & $\varnothing$ $+$stem$+$ \textipa{kat\super Si} & $\varnothing$ $+$stem$+$ \textipa{i} & $\varnothing$ $+$stem$+$ \textipa{1n} & $\varnothing$ $+$stem$+$ \textipa{e} & $\varnothing$ $+$stem$+$ \textipa{ita} & $\varnothing$ $+$stem$+$ \textipa{1ro} & UR
\\ \midrule
\textipa{pamman} & \textipa{pammaNk\super h1m} & \textipa{pamnar1m} & \textipa{pap} & \textipa{paptero} & \textipa{papkwa} & \textipa{pappota} & \textipa{papkat\super Si} & \textipa{papi} & \textipa{pap1n} & \textipa{pape} & \textipa{papita} & \textipa{pap1ro} &  -- \\
\textipa{summan} & \textipa{summaNk\super h1m} & \textipa{sumnar1m} & \textipa{sup} & \textipa{suptero} & \textipa{supkwa} & \textipa{suppota} & \textipa{supkat\super Si} & \textipa{sup\super hi} & \textipa{sup\super h1n} & \textipa{sup\super he} & \textipa{sup\super hita} & \textipa{sup\super h1ro} &  -- \\
\textipa{pamman} & \textipa{pammaNk\super h1m} & \textipa{pamnar1m} & \textipa{pam} & \textipa{pamtero} & \textipa{pamkwa} & \textipa{pampota} & \textipa{pamkat\super Si} & \textipa{pami} & \textipa{pam1n} & \textipa{pame} & \textipa{pamita} & \textipa{pam1ro} &  -- \\
\textipa{pamman} & \textipa{pammaNk\super h1m} & \textipa{pannar1m} & \textipa{pat} & \textipa{pattero} & \textipa{pakkwa} & \textipa{pappota} & \textipa{pakkat\super Si} & \textipa{pat\super S\super hi} & \textipa{pat\super h1n} & \textipa{pat\super he} & \textipa{pat\super S\super hita} & \textipa{pat\super h1ro} &  -- \\
\textipa{namman} & \textipa{nammaNk\super h1m} & \textipa{nannar1m} & \textipa{nat} & \textipa{nattero} & \textipa{nakkwa} & \textipa{nappota} & \textipa{nakkat\super Si} & \textipa{nasi} & \textipa{nas1n} & \textipa{nase} & \textipa{nasita} & \textipa{nas1ro} &  -- \\
\textipa{namman} & \textipa{nammaNk\super h1m} & \textipa{nannar1m} & \textipa{nat} & \textipa{nattero} & \textipa{nakkwa} & \textipa{nappota} & \textipa{nakkat\super Si} & \textipa{nat\super Si} & \textipa{nat\super S1n} & \textipa{nat\super Se} & \textipa{nat\super Sita} & \textipa{nat\super S1ro} &  -- \\
\textipa{namman} & \textipa{nammaNk\super h1m} & \textipa{nannar1m} & \textipa{nat} & \textipa{nattero} & \textipa{nakkwa} & \textipa{nappota} & \textipa{nakkat\super Si} & \textipa{nat\super S\super hi} & \textipa{nat\super S\super h1n} & \textipa{nat\super S\super he} & \textipa{nat\super S\super hita} & \textipa{nat\super S\super h1ro} &  -- \\
\textipa{pamman} & \textipa{pammaNk\super h1m} & \textipa{pannar1m} & \textipa{pan} & \textipa{pantero} & \textipa{paNkwa} & \textipa{pampota} & \textipa{paNkat\super Si} & \textipa{pani} & \textipa{pan1n} & \textipa{pane} & \textipa{panita} & \textipa{pan1ro} &  -- \\
\bottomrule\end{longtable}
\begin{tabular}{l}\emph{Rules: }\\
\textipa{t\super h} $\to$ \textipa{t\super S\super h} /  \verb|_| \textipa{i}\\\verb|[+coronal]| $\to$ $1$ /  \verb|_| \verb|[-continuant]|\\\verb|[ ]| $\to$ \verb|[-aspirated]| /  \verb|_| \{\verb|[-continuant]|,\#\}\\\textipa{p} $\to$ \textipa{m} /  \verb|_| \verb|[+nasal]|\\\verb|[+sibilant]| $\to$ \textipa{t} /  \verb|_| \#
\end{tabular}

\emph{Serbo--Croatian:}\\\begin{longtable}{llllllll|l}\toprule
$\varnothing$ $+$stem$+$ $\varnothing$ & $\varnothing$ $+$stem$+$ \textipa{a} & $\varnothing$ $+$stem$+$ \textipa{o} & $\varnothing$ $+$stem$+$ \textipa{i} & $\varnothing$ $+$stem$+$ \textipa{\'{e}m} & $\varnothing$ $+$stem$+$ \textipa{l} & $\varnothing$ $+$stem$+$ \textipa{l\'{a}} & $\varnothing$ $+$stem$+$ \textipa{lo} & UR
\\ \midrule
\textipa{ml\'{a}d} & \textipa{mlad\'{a}} & \textipa{mlad\'{o}} & \textipa{mlad\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{t\'{u}p} & \textipa{tup\'{a}} & \textipa{tup\'{o}} & \textipa{tup\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{bl\'{a}g} & \textipa{blag\'{a}} & \textipa{blag\'{o}} & \textipa{blag\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{gr\'{u}b} & \textipa{grub\'{a}} & \textipa{grub\'{o}} & \textipa{grub\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{kriZan} & \textipa{kriZana} & \textipa{kriZano} & \textipa{kriZani} &  --  &  --  &  --  &  --  &  -- \\
\textipa{sunt\super San} & \textipa{sunt\super Sana} & \textipa{sunt\super Sano} & \textipa{sunt\super Sani} &  --  &  --  &  --  &  --  &  -- \\
\textipa{svet\super San} & \textipa{svet\super Sana} & \textipa{svet\super Sano} & \textipa{svet\super Sani} &  --  &  --  &  --  &  --  &  -- \\
\textipa{b\'{e}o} & \textipa{bel\'{a}} & \textipa{bel\'{o}} & \textipa{bel\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{veseo} & \textipa{vesela} & \textipa{veselo} & \textipa{veseli} &  --  &  --  &  --  &  --  &  -- \\
\textipa{deb\'{e}o} & \textipa{debel\'{a}} & \textipa{debel\'{o}} & \textipa{debel\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{m\'{i}o} & \textipa{mil\'{a}} & \textipa{mil\'{o}} & \textipa{mil\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{zel\'{e}n} & \textipa{zelen\'{a}} & \textipa{zelen\'{o}} & \textipa{zelen\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{krad\'{e}n} & \textipa{kraden\'{a}} & \textipa{kraden\'{o}} & \textipa{kraden\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{dal\'{e}k} & \textipa{dalek\'{a}} & \textipa{dalek\'{o}} & \textipa{dalek\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{vis\'{o}k} & \textipa{visok\'{a}} & \textipa{visok\'{o}} & \textipa{visok\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{dub\'{o}k} & \textipa{dubok\'{a}} & \textipa{dubok\'{o}} & \textipa{dubok\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{bogat} & \textipa{bogata} & \textipa{bogato} & \textipa{bogati} &  --  &  --  &  --  &  --  &  -- \\
\textipa{rapav} & \textipa{rapava} & \textipa{rapavo} & \textipa{rapavi} &  --  &  --  &  --  &  --  &  -- \\
\textipa{j\'{a}san} & \textipa{jasn\'{a}} & \textipa{jasn\'{o}} & \textipa{jasn\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{v\'{a}Zan} & \textipa{vaZn\'{a}} & \textipa{vaZn\'{o}} & \textipa{vaZn\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{s\'{i}tan} & \textipa{sitn\'{a}} & \textipa{sitn\'{o}} & \textipa{sitn\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{ledan} & \textipa{ledna} & \textipa{ledno} & \textipa{ledni} &  --  &  --  &  --  &  --  &  -- \\
\textipa{t\'{a}nak} & \textipa{tank\'{a}} & \textipa{tank\'{o}} & \textipa{tank\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{kr\'{a}tak} & \textipa{kratk\'{a}} & \textipa{kratk\'{o}} & \textipa{kratk\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{bl\'{i}zak} & \textipa{blisk\'{a}} & \textipa{blisk\'{o}} & \textipa{blisk\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{\'{u}zak} & \textipa{usk\'{a}} & \textipa{usk\'{o}} & \textipa{usk\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{d\'{o}bar} & \textipa{dobr\'{a}} & \textipa{dobr\'{o}} & \textipa{dobr\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{\'{o}Star} & \textipa{oStr\'{a}} & \textipa{oStr\'{o}} & \textipa{oStr\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{bodar} & \textipa{bodra} & \textipa{bodro} & \textipa{bodri} &  --  &  --  &  --  &  --  &  -- \\
\textipa{ustao} & \textipa{ustala} & \textipa{ustalo} & \textipa{ustali} &  --  &  --  &  --  &  --  &  -- \\
\textipa{m\'{u}kao} & \textipa{mukl\'{a}} & \textipa{mukl\'{o}} & \textipa{mukl\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{\'{o}bao} & \textipa{obl\'{a}} & \textipa{obl\'{o}} & \textipa{obl\'{i}} &  --  &  --  &  --  &  --  &  -- \\
\textipa{p\'{o}dao} & \textipa{podl\'{a}} & \textipa{podl\'{o}} & \textipa{podl\'{i}} &  --  &  --  &  --  &  --  &  -- \\
 --  &  --  &  --  &  --  & \textipa{tep\'{e}m} & \textipa{t\'{e}pao} & \textipa{tepl\'{a}} & \textipa{tepl\'{o}} &  -- \\
 --  &  --  &  --  &  --  & \textipa{skub\'{e}m} & \textipa{sk\'{u}bao} & \textipa{skubl\'{a}} & \textipa{skubl\'{o}} &  -- \\
 --  &  --  &  --  &  --  & \textipa{tres\'{e}m} & \textipa{tr\'{e}sao} & \textipa{tresl\'{a}} & \textipa{tresl\'{o}} &  -- \\
 --  &  --  &  --  &  --  & \textipa{vez\'{e}m} & \textipa{v\'{e}zao} & \textipa{vezl\'{a}} & \textipa{vezl\'{o}} &  -- \\
\bottomrule\end{longtable}
\begin{tabular}{l}\emph{Rules: }\\
\verb|[+vowel]| $\to$ \verb|[+highTone]| / \verb|[+highTone]| \verb|[ ]|* \verb|_| \\$\varnothing$ $\to$ \textipa{a} / \verb|[-vowel]| \verb|_| \verb|[-vowel]| \#\\\verb|[+vowel]| $\to$ \verb|[-highTone]| /  \verb|_| \verb|[ ]|* \verb|[+highTone]|\\\textipa{l} $\to$ \textipa{o} /  \verb|_| \#\\\verb|[-sonorant]| $\to$ \verb|[-voice]| /  \verb|_| \verb|[-voice]|
\end{tabular}
